Analysis of competitive surfing tournaments with generalized Bradley-Terry

### 2021-08-25 inst/surfing_jsa.tex
hyperref as per https://editorialexpress.com/e-editor/pdftips.html
appearance changes as per instructions to authors

\documentclass{article}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}

@@

\begin{table}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l}
competitor  & nationality&wct01  &wct02  &wct03  & \ldots &wct09&wct10&wct11&points\\ \hline
 Ferreira   &   BRA      &   1   &   5   &   17  & \ldots      &  2   &   1   &   1   &   59740\\
 Medina     &   BRA      &   5   &   5   &   17  & \ldots      &  9   &   9   &   2   &   56475\\
 Smith 	    &   ZAF      &   3   &   3   &   17  & \ldots      &  9   &   2   &   17  &   49985\\
 Toledo     &   BRA      &   9   &   2   &   5   & \ldots      &  17  &   5   &   17  &   49145\\
 Andino     &   USA      &   2   &   17  &   5   & \dots       &  5   &   5   &   9   &   46655
\end{tabular}
\caption{WCT tour results, conventional league table\label{resultstable}}
\end{table}

@@

\begin{table}
\begin{verbatim}
wct01 Colapinto Bailey Wright
wct01 Freestone Lau Smith
wct01 Dora Ferreira Slater
wct01 Duru Toledo Ibelli
wct01 Moniz Heazlewood Wilson
...
wct11 Medina Florence
wct11 Colapinto Bourez
wct11 Ferreira Slater
wct11 Medina Colapinto
wct11 Ferreira Medina
\end{verbatim}
\caption{Extract from observations: raw results\label{rawresults} from
  WCT 2018}
\end{table}

The first line of table \ref{rawresults} shows that, at one of the
heats in {\tt wct01}, Colapinto came first, Bailey second, and Wright
came third.  The last line shows that, at {\tt wct11}, Ferreira came
first and Medina second.  We can convert this dataset into a
Plackett-Luce likelihood function but first have to remove the
wildcards and also player Vries whose maximum likelihood strength is
zero.  For the first line we would have Plackett-Luce likelihood function as

@@

\section{Results}
\begin{figure}
\includegraphics[width=4in]{surfing_files/figure-html/showsurfingmaxppie-3.png} % Pie chart of strengths
\caption{Pie chart\label{piechartmax} showing maximum likelihood strengths of the 23 competitors.  Note the
dominance of Ferreira, Florence, and Medina}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=4in]{surfing_files/figure-html/plotwidep-1.png}
\caption{Profile support \label{brazilian_wavetype_support} for the
  Brazilian wavetype reified entity.  The horizontal axis specifies a
  particular strength for Brazilian wavetype, and the height of the
  curve gives the support conditional on the x-axis}
\end{figure}

@@

\begin{table}
\begin{tabular}{l|l}
order  & ${\mathcal L}(p_1,p_2,q,p_C)$\\ \hline
$p_1\succ p_2\succ q $ & $ \frac{p_1}{p_1+p_2+q+p_C}\cdot\frac{p_2}{p_2+q+p_C}$\\
$p_2\succ p_1\succ q $ & $ \frac{p_2}{p_1+p_2+q+p_C}\cdot\frac{p_1}{p_1+q+p_C}$\\
$p_1\succ q\succ p_2 $ & $ \frac{p_1}{p_1+p_2+q+p_C}\cdot\frac{q+p_C}{p_2+q+p_C}$\\
$p_2\succ q\succ p_1 $ & $ \frac{p_2}{p_1+p_2+q+p_C}\cdot\frac{q+p_C}{p_1+q+p_C}$\\
$q\succ p_1\succ p_2 $ & $ \frac{q+p_C}{p_1+p_2+q+p_C}\cdot\frac{p_1}{p_1+p_2}$\\
$q\succ p_2\succ p_1 $ & $ \frac{q+p_C}{p_1+p_2+q+p_C}\cdot\frac{p_2}{p_1+p_2}$\\
\end{tabular}
\caption{The \label{likelihoodcompatriot} six possible finishing
  orders (``$\succ$'' means ``scored more points than'') for the case
  where two compatriot surfers and an odd man out are in the water at
  the same time, with associated likelihood function for strengths
  $p_1,p_2,q, p_C$.  Here $p_1,p_2$ are the strengths of two
  compatriot surfers, $q$ the strength of the odd man out, $p_C$ the
  strength of the compatriot monster. and nationality and a third are
  in the water at the same time}
\end{table}

@@

\bibliographystyle{agsm}
\bibliography{chess}
\end{document}

>>>>

\documentclass{article}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[pdftex]{hyperref}

@@

@@

Table~\ref{rawresults} shows the first few and last few entries in the
dataset we use.  The first line shows that, at one of the heats in
{\tt wct01}, Colapinto came first, Bailey second, and Wright came
third.  The last line shows that, at {\tt wct11}, Ferreira came first
and Medina second.  We can convert this dataset into a Plackett-Luce
likelihood function but first have to remove the wildcards and also
player Vries whose maximum likelihood strength is zero.  For the first
line we would have Plackett-Luce likelihood function as

@@

\section{Results}

@@

@@

@@

\bibliographystyle{agsm}
\bibliography{chess}

\clearpage
\newpage

\section*{Tables}

\begin{table}[h]
\begin{tabular}{llllllllllllll}
competitor  & nationality&wct01  &wct02  &wct03  & \ldots &wct09&wct10&wct11&points\\ \hline
 Ferreira   &   BRA      &   1   &   5   &   17  & \ldots      &  2   &   1   &   1   &   59740\\
 Medina     &   BRA      &   5   &   5   &   17  & \ldots      &  9   &   9   &   2   &   56475\\
 Smith 	    &   ZAF      &   3   &   3   &   17  & \ldots      &  9   &   2   &   17  &   49985\\
 Toledo     &   BRA      &   9   &   2   &   5   & \ldots      &  17  &   5   &   17  &   49145\\
 Andino     &   USA      &   2   &   17  &   5   & \dots       &  5   &   5   &   9   &   46655
\end{tabular}
\caption{WCT tour results, conventional league table\label{resultstable}}
\end{table}

\begin{table}[h]
\begin{verbatim}
wct01 Colapinto Bailey Wright
wct01 Freestone Lau Smith
wct01 Dora Ferreira Slater
wct01 Duru Toledo Ibelli
wct01 Moniz Heazlewood Wilson
...
wct11 Medina Florence
wct11 Colapinto Bourez
wct11 Ferreira Slater
wct11 Medina Colapinto
wct11 Ferreira Medina
\end{verbatim}
\caption{Extract from observations: raw results\label{rawresults} from
  WCT 2018}
\end{table}

\begin{table}[h]
\begin{tabular}{l|l}
order  & ${\mathcal L}(p_1,p_2,q,p_C)$\\ \hline
$p_1\succ p_2\succ q $ & $ \frac{p_1}{p_1+p_2+q+p_C}\cdot\frac{p_2}{p_2+q+p_C}$\\
$p_2\succ p_1\succ q $ & $ \frac{p_2}{p_1+p_2+q+p_C}\cdot\frac{p_1}{p_1+q+p_C}$\\
$p_1\succ q\succ p_2 $ & $ \frac{p_1}{p_1+p_2+q+p_C}\cdot\frac{q+p_C}{p_2+q+p_C}$\\
$p_2\succ q\succ p_1 $ & $ \frac{p_2}{p_1+p_2+q+p_C}\cdot\frac{q+p_C}{p_1+q+p_C}$\\
$q\succ p_1\succ p_2 $ & $ \frac{q+p_C}{p_1+p_2+q+p_C}\cdot\frac{p_1}{p_1+p_2}$\\
$q\succ p_2\succ p_1 $ & $ \frac{q+p_C}{p_1+p_2+q+p_C}\cdot\frac{p_2}{p_1+p_2}$\\
\end{tabular}
\caption{The \label{likelihoodcompatriot} six possible finishing
  orders (``$\succ$'' means ``scored more points than'') for the case
  where two compatriot surfers and an odd man out are in the water at
  the same time, with associated likelihood function for strengths
  $p_1,p_2,q, p_C$.  Here $p_1,p_2$ are the strengths of two
  compatriot surfers, $q$ the strength of the odd man out, $p_C$ the
  strength of the compatriot monster. and nationality and a third are
  in the water at the same time}
\end{table}

\clearpage
\newpage
\section*{Figures}

\begin{figure}[h]
\includegraphics[width=4in]{surfing_files/figure-html/showsurfingmaxppie-3.png} % Pie chart of strengths
\caption{Pie chart\label{piechartmax} showing maximum likelihood strengths of the 23 competitors.  Note the
dominance of Ferreira, Florence, and Medina}
\end{figure}

\begin{figure}[h]
  \includegraphics[width=4in]{surfing_files/figure-html/plotwidep-1.png}
\caption{Profile support \label{brazilian_wavetype_support} for the
  Brazilian wavetype reified entity.  The horizontal axis specifies a
  particular strength for Brazilian wavetype, and the height of the
  curve gives the support conditional on the x-axis}
\end{figure}

\end{document}
